What do incoming university students believe about open science practices in

### 2021-09-10 analysis/Manuscript.Rmd
moved histogram to supplemental

# # import the metadata [check if I need it for these analyses?]
# metadata <- here::here("survey", "data", "os_metadata_raw_data.csv") %>% 
#   read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
#   filter(!is.na(OldVariable))
```

@@

# gender --> need to summarise once we've recoded it in preprocessing script
  # [breadcrumb]
gender <- df %>% dplyr::count(gender)

@@

@@

p <- in_prac_long %>%
  ggplot(aes(x = `prevalence rating`)) +
  geom_histogram(aes(y=stat(count)), binwidth = 10) +
    xlab("Prevalence Ratings (%)") +
    ylab("Frequency") +
    facet_wrap(~practice)
p

@@

>>>>

# import the metadata 
metadata <- here::here("survey", "data", "students_metadata.csv") %>% 
 read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
 filter(!is.na(old_variable)) %>% 
 dplyr::select (-c("...10", "note:"))
```

@@

# gender --> need to summarise once we've recoded it in preprocessing script
gender <- df %>% dplyr::count(gender)

@@

# [breadcrumb Sept 10: pull in this info from the meta data]

# recode the data so the response options have proper labels

# c <- metadata %>% 
#     filter(Scale == "OSmost") %>% 
#     filter(NewVariable != "OSmost_text") #remove this value from metadata
# 
# d <- full_join(OSmost_long, c, by = c("OSmost" = "NewVariable")) %>% 
#   rename ("OSmost_label" = "ItemText")

@@

@@

# Supplemental Materials

Figure XX displays the histograms for each of the norms in practice items.

p <- in_prac_long %>%
  ggplot(aes(x = `prevalence rating`)) +
  geom_histogram(aes(y=stat(count)), binwidth = 10) +
    xlab("Prevalence Ratings (%)") +
    ylab("Frequency") +
    theme_classic () +
    theme(axis.text = element_text(size = 9), axis.title = element_text(size = 9)) +
    facet_wrap(~practice, nrow = 2)
p
